Synthesizing by means of mice with partially synthetic data rules

### 2021-09-26 mice_synthesizing/synthesizing_partially_synthetic_data_rules.Rmd

$$
\begin{aligned}
\nu_p &= (m - 1)(1 + \frac{\bar{u}_m}{\frac{b_m}{m}}) \\
&= (m - 1)(1 + \frac{m \cdot \bar{u}_m}{b_m}).
\end{aligned}
$$

@@

>>>>

$$
\begin{aligned}
\nu_p &= (m - 1)(1 + \frac{\bar{u}_m}{\frac{b_m}{m}})^2 \\
&= (m - 1)(1 + \frac{m \cdot \bar{u}_m}{b_m})^2.
\end{aligned}
$$

@@

```{r}
boot_cart_maxit_cp_min3 %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(~mice:::pool.syn(.x) %>% summary(conf.int = TRUE) %>% as.data.frame) %>%
  mutate(true_coef = rep(coef(truemodel), nrow(.) / length(coef(truemodel))),
         covered = `2.5 %` < true_coef & true_coef < `97.5 %`) %>%
  group_by(term) %>%
  summarize(estimate = mean(estimate),
            bias = mean(estimate - true_coef),
            var = mean(std.error^2),
            lower = mean(`2.5 %`),
            upper = mean(`97.5 %`),
            coverage = mean(covered), .groups = "drop") %>%
    kable(digits = 3,
        caption = "Synthetic regression estimates after bootstrapping, 
        synthesizing (with adjusted mice CART settings) and analysing
        the boys dataset 500 times") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

boot_cart_cp_min3 %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(~mice:::pool.syn(.x) %>% summary(conf.int = TRUE) %>% as.data.frame) %>%
  mutate(true_coef = rep(coef(truemodel), nrow(.) / length(coef(truemodel))),
         covered = `2.5 %` < true_coef & true_coef < `97.5 %`) %>%
  group_by(term) %>%
  summarize(estimate = mean(estimate),
            bias = mean(estimate - true_coef),
            var = mean(std.error^2),
            lower = mean(`2.5 %`),
            upper = mean(`97.5 %`),
            coverage = mean(covered), .groups = "drop") %>%
  kable(digits = 3,
        caption = "Synthetic regression estimates after bootstrapping, 
        synthesizing (with adjusted mice CART settings) and analysing
        the boys dataset 500 times") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```
